\ifxHPTDC{
    \newcommand{\device}{}
    \newcommand{\deviceindex}{\cronvar{int}{index}}
    \newcommand{\deviceconfig}{}
    \newcommand{\initparameters}{xhptdc8\tu manager\tu init\tu parameters}
}{
    \newcommand{\device}{\cronvar{\prefix device}{*device}}
    \newcommand{\deviceindex}{\device}
    \newcommand{\deviceconfig}{\deviceindex, }
    \newcommand{\initparameters}{\prefix init\tu parameters}
}

The API is a DLL with C linkage.\par

The functions provided by the driver are declared in
\texttt{\txh{TimeTagger4}{xTDC4}{xHPTDC8}\tu interface.h} 
which must be included by your source code.
You must tell your compiler to link with the file
\ifxHPTDC{%
    \texttt{xhptdc8\tu driver.lib} or the corresponding 64 bit version
    \texttt{xhptdc8\tu driver\tu 64.lib}.
}{%
    \textsf{xTDC4\tu driver\tu 64.lib}.}
When running your program the dynamic link library containing the actual
driver code must reside in the same directory as your executable or be in a
directory included in the PATH variable. For Linux, it is provided only as a
static library \texttt{libxtdc4\tu driver.a} 
The file for the DLL is called \texttt{xTDC4\tu driver\tu 64.dll}.

All these files are provided with the driver installer that can be downloaded
from the product website \href{https://www.cronologic.de}{www.cronologic.de}. 
By default, the installer will place the files into the directory 
\texttt{C:\filesep Program Files\filesep cronologic\filesep \deviceName\filesep driver}.
A coding example can be found on\\
\href{https://github.com/cronologic-de/xtdc_babel/tree/main/timetagger4_user_guide_example}{github.com/cronologic-de/xtdc\_babel}.

\ifxHPTDC{
    There exist an open-source community project that intends to provide some
    convenient extensions to the driver, code examples, and wrappers to make
    the driver usable with various programming languages like Python and
    LabView. The project is hosted at
    \url{https://github.com/cronologic-de/xhptdc8_babel}.
}{}

 
\section{Constants}
\ifxHPTDC{
    \begin{description}[style=nextline]
        \item[\crondef{XHPTDC8\tu MANAGER\tu DEVICES\tu MAX 6}]
        The maximum number of boards supported by the device manager.

        \item[\ttdef{TDC\tu CHANNEL\tu COUNT 8}]
        The number of TDC input channels.

        \item[\ttdef{GATE\tu COUNT 8}]
        The number of gating blocks. One for each TDC input.

        \item[\ttdef{TIGER\tu COUNT 9}]
        The number of timing generators. One for each TDC input and one for the
        ADC trigger.

        \item[\ttdef{TRIGGER\tu COUNT 16}]
        The number of potential trigger sources for the timing generators. One
        for each TDC input \ifxHPTDC{}{, one for the Start input} plus some
        specials.  See Section~\ref{structtrigger} for details.
}{ 
    \begin{description}[style=nextline]
        \item[\ttdef{TDC\tu CHANNEL\tu COUNT 4}]
        The number of TDC input channels.

        \item[\ttdef{TIGER\tu COUNT 5}]
        The number of timing generators. One for each TDC input and one for the
        start input.

        \item[\ttdef{TRIGGER\tu COUNT 16}]
        The number of potential trigger sources for the timing generators. One
        for each TDC input, one for the Start input plus some specials. See
        Section~\ref{cp:tigerblock} for details. 
}
    \item[\ttdef{OK 0}]
    Error codes are set by the API functions to this value if there has
    been no error. Other error codes can be found in
    \texttt{\txh{TimeTagger4}{xTDC4}{xHPTDC8}\tu interface.h}
\end{description}





\section{Driver Information}
Even if there is no board present the driver revision can be queried using
these functions.

\begin{description}[style=nextline]
    \item[\ttvar{int}{get\tu driver\tu revision()}]
    Returns the driver version, same format as \texttt{\prefix static\tu
    info.driver\tu revision}.  This function does not require \adeviceName\
    board to be present.

    \item[\ttvar{const char*}{get\tu driver\tu revision\tu str()}]
    Returns the driver version including SVN build revision as a string. 

    \item[\ttvar{int}{count\tu devices(}\cronvar{int}{*error\tu code},
    \cronvar{char}{**error\tu message)}\label{countdevices}]
    Returns the number of boards present in the system that are supported by
    this driver.  Pointers to an error code and message variable have to be
    provided. If {\ttfamily error\_code} does not equal
    {\ttfamily\ttdef{OK} = 0}, the error message will contain what went wrong.
    E.g., crono kernel was not properly installed. \par
\end{description}




\section{Initialization}
The card must be initialized first before reading data. Normally the process is
to get the default init parameters and change some values. E.g., choose one of
multiple cards by the index or use a larger buffer.
    

\begin{description}[style=nextline]
    \item[\ttvar{int}{get\tu default\tu init\tu
        parameters(}\cronvar{\initparameters}{*init)}]
    Sets up the standard parameters. Gets a set of default parameters for
    \texttt{\prefix init()}.  This must always be used to initialize the
    \texttt{\initparameters} structure before modifying it and passing it to
    \texttt{\prefix init}.

    \ifxHPTDC{
        \item[\ttvar{int}{init(}\cronvar{\initparameters}{*params})]
    }{
        \item[\cronvar{\prefix device}{\prefix
            init(}\cronvar{\initparameters}{*params}, \cronvar{int}{*error\tu
            code}, \cronvar{char}{**error\tu message)}]
    }
    Opens and initializes the \deviceName\ 
    \ifxHPTDC{boards in the system}{board with the given index}. \par
    \ifxHPTDC{
        If the return value does not equal {\ttfamily\ttdef{OK} = 0}
        the device initialization failed.
    }{
        \texttt{error\tu code} must point to an integer where the driver can 
        write the error code.\par
        \texttt{error\tu message} must point to a pointer to char.  The driver
        will allocate a buffer for zero-ter\-mi\-na\-ted error message and 
        store the address of the buffer in the location provided by the
        user.\par
    }
    The parameter \texttt{params} is a pointer to a structure of
    type \texttt{\initparameters} that must be completely initialized by
    \texttt{get\tu default\tu init\tu parameters()}.

    \item[\ttvar{int}{close(}\device )]
    Closes the devices, releasing all resources. 
\end{description}

%%%%%%%%%%%%%%%%% struct init_parameters

\subsection{Structure \initparameters}
\begin{description}[style=nextline]
    \item[\cronvar{int}{version}\txhinits{}{}{\PREFIX API\tu VERSION}]
    The version number. Must be set to \texttt{\PREFIX API\tu VERSION}.\par

    \ifxHPTDC{}{
        \item[\cronvar{int}{card\tu index}]
        The index in the list of \deviceName\ boards that should be
        initialized.\par
        There might be multiple boards in the system that are handled by this
        driver as reported by \texttt{\prefix count\tu devices}. This index
        selects one of them. Boards are enumerated depending on the PCIe slot.
        The lower the bus number and the lower the slot number the lower the
        card index.

        \item[\cronvar{int}{board\tu id}]
        The global index in all cronologic devices.\par
        This 8-bit number is filled into each packet created by the board and
        is useful if data streams of multiple boards will be merged. If only
        \deviceName\ cards are used this number can be set to the
        \texttt{card\tu index}.  If boards of different types that use a
        compatible data format are used in a system each board should get a
        unique id.  Can be changed with \texttt{int \prefix set\tu board\tu
        id\allowbreak(\prefix device *device, int board\tu id)}.}


    \item[\cronvar{uint64\tu t}{buffer\tu size\ifxHPTDC{}{[8]}}%
        \txhinits{}{}{XHPTDC\_DEFAULT\_BUFFER\_SIZE}%
        \txh{}{}{\normalfont\ttfamily\ // 0x1000000 (16 MB)}]
    The minimum size of the DMA buffer.\\
    If set to \texttt{0} the default size of 16\,MByte is used. 
    \ifxHPTDC{}{For the \deviceName\ only the first entry is used.}\par

    \ifxHPTDC{}{
        \item[\cronvar{int}{buffer\tu type}]
        The type of buffer. Must be set to \texttt{0}.
        \begin{description}
            \item[]  \ttdef{BUFFER\tu ALLOCATE   0}
            \item[]  \ttdef{BUFFER\tu USE\tu PHYSICAL   1}  // unsupported
        \end{description}

        \item[\cronvar{uint64\tu t}{buffer\tu address}]
        This is set by \texttt{\prefix init()} to the start address of the
        reserved memory.\par
        The buffers will be allocated with the sizes given above. Make sure
        that the memory is large enough.
    }

    \item[\cronvar{int}{variant}\txhinits{0}{0}{0}]
    Set to \texttt{0}. Can be used to activate future device variants such as
    different base frequencies.\par

    \item[\cronvar{int}{device\tu type}\txhinits{}{}{CRONO\_DEVICE\_XHPTDC8}]
    A constant for the different devices of cronologic
    \texttt{CRONO\tu DEVICE\tu *}.\par
    Initialized by \texttt{\prefix get\tu default\tu init\tu parameters()}.
    This value is identical to the PCI Device ID. Must be left unchanged.

    \begin{tabular}{ll}
        \crondef{CRONO\tu DEVICE\tu HPTDC}       & \ttfamily 0x1 \\
        \crondef{CRONO\tu DEVICE\tu NDIGO5G}     & \ttfamily 0x2 \\
        \crondef{CRONO\tu DEVICE\tu NDIGO250M}   & \ttfamily 0x4 \\
        \crondef{CRONO\tu DEVICE\tu xTDC4}       & \ttfamily 0x6 \\
        \crondef{CRONO\tu DEVICE\tu TIMETAGGER4} & \ttfamily 0x8 \\
        \crondef{CRONO\tu DEVICE\tu XHPTDC8}     & \ttfamily 0xC \\
        \crondef{CRONO\tu DEVICE\tu NDIGO6}      & \ttfamily 0xD \\
    \end{tabular}

    \item[\cronvar{int}{dma\tu read\tu delay}\txhinits{}{}{250}]
    The update delay of the write pointer after a packet has been sent over
    PCIe. Specified in multiples of \SI{16}{\nano\second}.  Should not be
    changed by the user.

    \ifxHPTDC{
        \item[\cronvar{crono\tu bool\tu t}{multiboard}\txhinits{}{}{false}]
        Set if multiple devices shall be synchronized. Also sets the clock
        source to external.

        \item[\cronvar{crono\tu bool\tu t}{use\tu ext\tu clock}%
            \txhinits{}{}{false}]
        If set use the external 10\,MHz reference on J2, otherwise the internal
        clock source is used.  When \texttt{multiboard} is set, this parameter
        is ignored and the external clock is used. 

        \item[\cronvar{crono\tu bool\tu t}{ignore\tu calibration}%
            \txhinits{}{}{false}]
        Leave at \texttt{false} to use device calibration data.

    }{
        \item[\cronvar{int}{use\tu ext\tu clock}]
        If set to \texttt{1}, use external 10\,MHz reference. If set to
        \texttt{0}, use internal reference.
    }
\end{description}

% info structures
\input{common/InfoStructs.tex}



\section{Configuration}
\ifxHPTDC{
    All \deviceName\ boards in the system are configured by a single
    configuration structure which in turn contains sub structures that
    configure the individual boards.
}{
    The device is configured with a configuration structure.
}
The user should first obtain a structure that contains the default settings of
the device read from an on-board ROM, then modify the structure as needed for
the user application and use the result to configure the device.\par

\begin{description}[style=nextline]
    \item[\ttvar{int}{configure(}\deviceconfig\cronvar{\prefix\ifxHPTDC{manager\tu }{}configuration}{*config)}]
    Configures the \texttt{\prefix manager}.

    \item[\protect{\parbox[b]{1.0\linewidth}{
        \ttvar{int}{get\tu current\tu configuration(}\deviceconfig
        \ifxHPTDC{}{\hspace*{\labelwidth+\itemsep}}\cronvar{
            \prefix\ifxHPTDC{manager\tu }{}configuration}{\textbf{*config})}}}]
    Gets current configuration. Copies the current configuration to the
    specified config pointer.

    \item[\protect{\parbox[b]{1.0\linewidth}{
        \ttvar{int}{get\tu default\tu configuration(}\deviceconfig
        \ifxHPTDC{}{\hspace*{\labelwidth+\itemsep}}\cronvar{
            \prefix \ifxHPTDC{manager\tu}{}configuration}{\textbf{*config})}}}]
    Gets default configuration. Copies the default configuration to the
    specified config pointer.
\end{description}

\ifxHPTDC{
    \subsection{YAML config files}
    \label{yaml}
    There exist a community maintained utility library for the \deviceName\
    that contains a convenience function that can modify configuration
    structures from a YAML config string. This can significantly shorten code
    required to setup the TDC. \par
    See \href{https://github.com/cronologic-de/xhptdc8_babel/tree/main/util}{
        github.com/cronologic-de/xhptdc8\tu babel/tree/main/util} for details.  
}{} 

%%%%%%%%%%%%%%%%% configuration structure mostly shared between devices
\input{common/StructConfig.tex}


%%%%%%%%%%%%%%

\ifxHPTDC{
    \section{User Data Storage}
    There is a 64~kByte flash memory on each board that users can utilize to
    store any type of data.  A typical use case would be calibration data for
    the \deviceName\ or the detectors that the device is connected to.  Also
    serial numbers of instruments built with the \deviceName\ can be stored
    here. Write operations always erase the whole memory block.\par

    \begin{description}[style=nextline]
        \item[\ttdef{USER\tu FLASH\tu SIZE 0x10000}]
        The size of the flash memory in bytes.\\

        \item[\protect{\parbox[b]{1.0\linewidth}{
            \ttvar{int}{read\tu user\tu flash(\cronvar{int}{index}, \cronvar{\uchar *}{flash\tu data}, \cronvar{\uint}{size})}\\
            \ttvar{int}{write\tu user\tu flash(\cronvar{int}{index}, \cronvar{\uchar *}{flash\tu data}, \cronvar{\uint}{size})}
        }}]
        Read from or write to the user flash of a board identified by
        \texttt{index}.  \texttt{flash\tu data} must point to a buffer
        allocated by the user.  \texttt{size} must specify the size of that
        buffer in bytes.  We recommend to always allocate a buffer of the size
        of the flash memory given by \texttt{\PREFIX FLASH\tu SIZE} to clarify
        that always the full buffer is overwritten.
    \end{description}
}{} 


    
