% SVN Info:
% $Date: 2021-01-29 22:28:41 +0100 (Fr, 29 Jan 2021) $
% $Rev: 1039 $
% $Author: kolja $

\clearpage
\section{Electrical Characteristics}

\subsection{Power Supply}

\noindent
\begin{tabularx}{\textwidth}{|c|X|c|c|c|c|}
    \hline
    Symbol & Parameter & Min & Typical & Max & Units\\
    \hline\hline
    P\subscript{total} & Total power consumption & & & \ifxHPTDC{20}{10}& \si{\watt}\\
    \hline
    VCC\subscript{3.3} & PCIe \SI{3.3}{\volt} rail power supply voltage &3.1&3.3&3.5& \si{\volt}\\
    \hline
    I\subscript{3.3} & PCIe \SI{3.3}{\volt} rail input current & & &\txh{650}{600}{600}& \si{\milli\ampere}\\
    \hline
    VCC\subscript{12} & PCIe \SI{12}{\volt} rail power supply voltage &11.1&12.0&12.9& \si{\volt}\\
    \hline
    I\subscript{12} & PCIe \SI{12}{\volt} rail input current & & & \txh{550}{650}{1500} & \si{\milli\ampere}\\
    \hline
    VCC\subscript{aux} & PCIe 3.3\,V\subscript{Aux} rail power supply voltage &&3.3&& \si{\volt}\\
    \hline
    I\subscript{aux} & PCIe 3.3\,V\subscript{Aux} rail input current &&0&& \si{\milli\ampere}\\
    \hline
\end{tabularx}

\subsection{TDC Inputs} \label{din:tdcinputs}
The \deviceName's inputs are single-ended AC-coupled with 50\,Ω termination.

\noindent
\begin{tabularx}{\textwidth}{|c|X|c|c|c|c|}
    \hline
    Symbol & Parameter & Min & Typical & Max & Units\\
    \hline\hline
    V\subscript{Base} & Input Baseline & 0 & & 5 & \si{\volt}\\
    \hline
    V\subscript{Threshold} & Trigger Level & V\subscript{Base} $-$ \dcminabs & & V\subscript{Base} + \dcmax & \si{\volt}\\
    \hline
    |ΔV\subscript{min}| & Magnitude of minimal pulse height & \ifxHPTDC{100}{10} & & & \si{\milli\volt}\\
    \hline
    \itett{
        t\subscript{Pulse} & Pulse Length\newline
            \hfill --1.25G\newline
            \hfill --2.5G\newline
            \hfill --5G\newline
            \hfill --10G
        & \makecell[tc]{\mbox{}\\0.8\\0.4\\0.2\\0.1} & 5 & 200 & \si{\nano\second}
    }
    {
        t\subscript{Pulse} & Pulse Length & 2 & 5 & 200 & \si{\nano\second}
    }\\
    \hline
    t\subscript{Rise} & Pulse Edge 20\% to 80\%  &  &  & 10 & \si{\nano\second}\\
    \hline
    t\subscript{Fall} & Pulse Edge 80\% to 20\%  &  &  & 10 & \si{\nano\second}\\
    \hline
    Z\subscript{P} & Input Impedance && 50 && Ω\\
    \hline
    I\subscript{Term} & Termination Current & --50 & --20 & 50 & \si{\milli\ampere}\\
    \hline
\end{tabularx}

All inputs are AC-coupled. The inputs have very high input bandwidth
requirements and therefore there are no circuits that provide over-voltage
protection for these signals.  Any voltage on the inputs above \SI{5}{\volt}
or below \SI{-5}{\volt} relative to the voltage of the slot cover can result
in permanent damage to the board.\par Keep in mind, that the input baseline
\textsf{V\subscript{Base}} is affected by the ratio of pulse length
\textsf{t\subscript{Pulse}} to average pulse distance (for continuous signals
the term is called duty cycle).\par

\ifxHPTDC{
    All digital inputs can output AC coupled pulses from the TiGer.  Special
    care should be taken not to enable the TiGer output when sensitive
    equipment is connected that could be damaged by the pulses. 
}{
    Make sure not to drive the inputs when the connector is configured as a
    TiGer output.\par 
}
See Section \ref{cp:tiger}. 

%%%%%%%%%%% ADC input
\ifxHPTDC{
    \newpage
    \subsection{ADC Inputs}
    The ADC input is DC coupled to a differential termination voltage of
    400\,mV.  This means that the actual voltage seen by the ADC will depend on
    the output impedance of the source that is driving the input.\par
    \noindent
    \begin{tabularx}{\textwidth}{|c|X|c|c|c|c|}
        \hline
        Symbol & Parameter & Min & Typical & Max & Units\\
        \hline\hline
        V\subscript{in} & Input voltage & --2.0 &  & 2.5 & V \\
        \hline 
        V\subscript{term} & Termination voltage & & 0.4 & & V \\
        \hline 
        Z\subscript{in} & Input Impedance & & 50  & & Ω \\
        \hline
    \end{tabularx}

    %%%%%%%%%%% clock input		
    \subsection{Clock input J2}
    The clock input J2 is single ended and AC coupled.\\*
    \noindent
    \begin{tabularx}{\textwidth}{|c|X|c|c|c|c|}
        \hline
        Symbol & Parameter & Min & Typical & Max & Units\\
        \hline\hline
        V\subscript{p-p} & Peak to Peak voltage & 1 &  & 3.3 & V \\
        \hline 
        V\subscript{cm} & Common mode voltage voltage &--3 &   & 3 & V \\
        \hline 
        V\subscript{tck} & Clock termination voltage & & 0 &  & V \\
        \hline 
        Z\subscript{in} & Input Impedance & & 50  & & Ω \\
        \hline 
        D\subscript{J2} & Duty cycle & 45 & 50 & 55 & \% \\
            \hline 
            f\subscript{J2}& Frequency &  & 10 &  & MHz \\
        \hline
    \end{tabularx}
}{}

\newpage
\section{Information Required by DIN EN 61010-1}
\subsection{Manufacturer\label{cp:manu}}

The \deviceName\ is a product of:\

\begin{quote}
    cronologic GmbH \& Co. KG\\
    Jahnstra\ss{}e 49\\
    60318 Frankfurt\par
    Germany
    \noindent HRA 42869 beim Amtsgericht Frankfurt/M\par
    \noindent VAT-ID: DE235184378 \\*
    \noindent PCI Vendor ID: 0x1A13
\end{quote}

\subsection{Intended Use and System Integration}
The devices are not ready to use as delivered by cronologic. It requires the
development of specialized software to fulfill the application of the
end-user. The device is provided to system integrators to be built into
measurement systems that are distributed to end users. These systems usually
consist of the \deviceName, a main board, a case, application software and
possibly additional electronics to attach the system to some type of detector.
They might also be integrated with the detector.\par

The \deviceName\ is designed to comply with DIN EN 61326-1 when operated on a
PCIe compliant main board housed in a properly shielded enclosure.  When
operated in a closed standard compliant enclosure the device does not pose any
hazards as defined by EN 61010-1.\par

Radiated emissions, noise immunity, and safety highly depend on the quality of
the enclosure.  It is the responsibility of the system integrator to ensure
that the assembled system is compliant to applicable standards of the country
that the system is operated in, especially regarding user safety and
electromagnetic interference. \par
    
When handling the board, adequate measures must be taken to protect the
circuits against electrostatic discharge (ESD). All power supplied to the
system must be turned off before installing the board.

\subsection{Environmental Conditions for Storage}
The board shall be stored between operation under the following conditions:

\noindent
\begin{tabularx}{\textwidth}{|c|X|c|c|c|c|}
    \hline
    Symbol & Parameter & Min & Typical & Max & Units\\
    \hline\hline
    T\subscript{store} & ambient temperature & --30 && 60 & \si{\degreeCelsius}\\
    \hline
    RH\subscript{store} & relative humidity at 31$^{\circ}$C noncondensing & 10 && 70 & \%\\
    \hline
\end{tabularx}

\clearpage
\subsection{Environmental Conditions for Operation}
The board is designed to be operated under the following conditions:

\noindent
\begin{tabularx}{\textwidth}{|c|X|c|c|c|c|}
    \hline
    Symbol & Parameter & Min & Typical & Max & Units\\
    \hline\hline
    T\subscript{oper} & ambient temperature & 5 && 40 & \si{\degreeCelsius}\\
    \hline
    RH\subscript{oper} & relative humidity at 31$^{\circ}$C & 20 && 75 & \%\\
    \hline
\end{tabularx}

WARNING: Do not connect any DC-coupled inputs to a channel while the TiGer of
that channel is configured as an output (see Section~\ref{cp:tiger}).  Doing
so could permanently damage the \deviceName\ and the external hardware.

\subsection{Cooling}
The \deviceName\ in its base configuration has passive cooling that requires a
certain amount of air-flow.  If the case design can't provide enough air-flow
to the board, a slot cooler like Zalman ZM-SC100 can be placed next to the
board.  Active cooling is also available as an option for the board.


\subsection{Recycling}
cronologic is registered with the ``Stiftung Elektro-Altgeräte Register''
as a manufacturer of electronic systems with Registration ID DE 77895909.\par
The \deviceName\ belongs to category 6, ``Kleine Geräte der Informations- und
Telekommunikationstechnik für die ausschließliche Nutzung in anderen als
privaten Haushalten.''  Devices sold before 2018 belong to category 9,
``Überwachungs und Kontrollinstrumente für ausschließlich
gewerbliche Nutzung.'' The last owner of a \deviceName\ must recycle it,
treat the board in compliance with \S{}11 and \S{}12 of the German ElektroG,
or return it to the manufacturer's address listed on Page~\pageref{cp:manu}.