\txh{ %TimeTagger Version
The \deviceName\ is a ``classic'' common start time-to-digital converter. 

It records the time difference between a leading or trailing edge on the start input to the leading and trailing edges of the stop inputs. 
Rising and falling edges of the stop channels A-D can be enabled individually. 
The measurements are quantized as shown in section \ref{sec:features}. 
The timestamps are recorded in integer multiples of the corresponding bin size.
Transitions of the input signals are called hits. To reliably detect hits the signal has to be stable for more than one quantisation interval before and after the edge.  
Triggers on the start channel must not occur less than \SI{5}{\nano\second} apart. The \deviceName\ records events without dead time at a readout rate of about 48\,MHits/s for Gen\,1 and 60\,MHits/s for Gen\,2.
} { %xTDC4 and xHPTDC8 Version
The \deviceName\ is a ``classic'' common start time-to-digital converter. 

It records the time difference between leading or trailing edges on the start input and the stop inputs. 
Each stop channel A-D can be enabled individually. 
The standard deviation of the timestamps is approx. \SI{8}{\pico\second}. 
The timestamps are recorded in integer multiples of a bin size of $5000/(3\cdot 128)$ = $13.0208\overline{3}$\,\si{\pico\second}. 
The data acquisition can be limited to rising or falling signal transitions. 

The maximum trigger rate on the start channel is \SI{4}{\mega\hertz}.

\subsection{Handling of Difficult Hits}
    \label{difficulthits}
    Transitions of the input signals are called hits. To measure all hits with the maximum resolution the hits must fulfill all criteria set forth in this document.
    However, the \deviceName does include mechanisms to provide as much information as possible for hits that fall out of these specs.

    To reliably detect hits the signal has to be stable for at least \SI{900}{\pico\second} before and after the edge that is to be measured. 
    Pulses as short as \SI{250}{\pico\second} are usually detected at full resolution but have a significant chance to be assigned to the wrong group or appear out of order. 
    For these hits bit 7 in the data word is set. See section \ref{flags} for more information on the data format.

    Between multiple hits on a stop channel a dead time of approximately \SI{5}{\nano\second} is required for full resolution. 
    Hits that are closer together will only be reported with a resolution of $5/6$\,\si{\nano\second} = $833\overline{3}$\,\si{\pico\second}. For these hits both bits 6 and 7 are set.

    Data is copied from the 15-entry L0 FIFO to the larger downstream FIFOs at a rate of about \SI{12}{\mega\hertz} per channel. 
    If the L0 FIFO overflows the high resolution measurement of some hits will be discarded. 
    In this case a measurement from an alternative TDC will be used that has a resolution of about \SI{150}{\pico\second}. 
    For these hits bit 6 in the data word will be set
} { %xHPTDC8 version
    The \deviceName\ is a streaming time-to-digital converter. It records the timestamps of changes at the inputs A-H in an infinite stream. 
    A flexible grouping mode is available that can emulate common-start or common-stop behaviour. See section \ref{grouping} for details.

    For each channel, it can be selected individually whether rising or falling edges are recorded. It is not possible to record both edges of the same channel. 
    The timestamps are recorded in integer multiples of a bin size of $5000/(3\cdot 128)$ = $13.0208\overline{3}$\,\si{\pico\second}. 
    There must be at least \SI{5}{\nano\second} between consecutive hits on the same input channel to be detected reliably. 
    The \deviceName\ records events without dead time at a readout rate of about $48$\,MHits/s.
}