\section{Output Structure crono\tu packet}

Output of a read call list is a group of \texttt{crono\tu packet} structures.
Which have a variable length. The structure contains the following fields.
    
\begin{description}[style=nextline]
    \item[\cronvar{uint8\tu t}{channel}]
    Index of the source channel of the data. Pseudo channel 15 is used for
    rollovers.\par

    \item[\cronvar{uint8\tu t}{card}]
    Identifies the source card in case there are multiple boards present. 
    Defaults to \texttt{0} if no value is assigned to the parameter
    \texttt{board\tu id} in structure
    \texttt{timetagger4\tu init\tu parameters}.

    \item[\cronvar{uint8\tu t}{type}]
    The data stream consists of 32-bit unsigned data as signified by 
    \texttt{CRONO\tu PACKET\tu TYPE\tu 32\tu BIT\tu UNSIGNED = 6}.

    \item[\cronvar{uint8\tu t}{flags}]
    Bit field of \textsf{TIMETAGGER4 \tu PACKET\tu FLAG\tu*}\,bits: \par

    \texttt{\ttdef{PACKET\tu FLAG\tu ODD\tu HITS} 1}\\
    If this bit is set, the last data word in the data array consists of one
    timestamp only which is located \indent in the lower 32 bits of the 64-bit
    data word (little endian).\par

    \texttt{\ttdef{PACKET\tu FLAG\tu SLOW\tu SYNC} 2}\\
    Timestamp of a hit is above the range of 8-bit rollover number and 24-bit
    hit timestamp. The group \indent is closed, all other hits are ignored.\par

    \texttt{\ttdef{PACKET\tu FLAG\tu START\tu MISSED} 4}\\
    The trigger unit has discarded packets due to a full FIFO because the data
    rate is too high. Starts are \indent missed and stops are potentially in
    wrong groups. \par

    \texttt{\ttdef{PACKET\tu FLAG\tu SHORTENED} 8}\\
    The trigger unit has shortened the current packet due to a full pipeline
    FIFO because the data rate is \indent too high. Stops are missing in the
    current packet.\par

    \texttt{\ttdef{PACKET\tu FLAG\tu DMA\tu FIFO\tu FULL} 16}\\
    The internal DMA FIFO was full. This is caused either because the data
    rate is too high on too many channels. Packet loss is possible.\par

    \texttt{\ttdef{PACKET\tu FLAG\tu HOST\tu BUFFER\tu FULL} 32}\\
    The host buffer was full. Might result in dropped packets. This is caused
    either because the data rate is too high or by data not being retrieved
    fast enough from the buffer. Solutions are increasing buffer size if the
    overload is temporary or by avoiding or optimizing any additional
    processing in the code that reads the data.\par

    \item[\cronvar{uint32\tu t}{length}]
    Number of 64-bit elements (each containing up to 2 TDC hits) in the data
    array. The number of hits contained is equal to
    \texttt{2 * length -
    (flags \& PACKET\tu FLAG\tu ODD\tu HITS) ? 1 : 0}.\par

    \item[\cronvar{uint64\tu t}{timestamp}]
    Coarse timestamp of the start pulse. Values are given in multiples of
    \itett{
        \texttt{packet\tu binsize} contained in
        \texttt{timetagger4\tu param\tu info}.
    }{
        $5/3=1.\overline{6}$\,\si{\nano\second}.
    }\par

    \item[\cronvar{uint64\tu t}{data[1]}]
    Contains the TDC hits as a variable length array (length can be zero). The
    user can cast the array to \texttt{uint32\tu t*} to directly operate on
    the TDC hits. For the number of hits, see length. Structure of one hit (32
    bit):
    \par
    \begin{small}
    \begin{center}
        \begin{tabular}{|c||p{9cm}|p{1,5cm}|p{1,5cm}|}
            \hline
            bits & 31\hfill to\hfill 8 & 7\hfill to \hfill 4 & 3\hfill to\hfill 0\\\hline
            content & TDC DATA & FLAGS & CHN \\\hline
        \end{tabular}
    \end{center}
    \end{small}\par

    The timestamp of the hit is stored in bits 31 down to 8 in multiples of 
    \itett{
        \texttt{binsize} contained in 
        \texttt{timetagger4\tu param\tu info.}
    }{
        $5/(3*128) = 13.0208\overline{3}$\,\si{\pico\second}
    }
\begin{verbatim}
uint32_t timestamp  = (hit >> 8) & 0xFFFFFF;
uint32_t flags      = (hit >> 4) & 0xF;
uint32_t channel    =  hit       & 0xF;
\end{verbatim}
    
    \label{flags}
    Bits 7 down to 4 are hit flags and have the following definitions:
    \itett{
        \begin{itemize}
            \item Bit 7: Not applicable for the \deviceName\ and therefore
            always \texttt{0}.

            \item \ttdef{HIT\tu FLAG\tu COARSE\tu TIMESTAMP}~\texttt{4}~$\leftrightarrow$
            Bit\,6\\
            Bit 6: Always \texttt{1} for the \deviceName.\\

            \item \ttdef{HIT\tu FLAG\tu TIME\tu OVERFLOW}~\texttt{2}~$\leftrightarrow$
            Bit\,5\\
            Bit 5: If set, this hit is a rollover. The time since the
            start pulse exceeded the 24-bit range that can be encoded in a
            data word. This word does not encode a measurement. Instead,
            the readout software should increment a rollover counter that can
            be used as the upper bits of consecutive time stamps.  The
            counters must be reset for each packet.  The total offset of a hit
            in picoseconds can be computed by
            \begin{align*}
                \Delta T_{hit} = &\,(\mathrm{\#{}rollovers} \times \texttt{timetagger4\_static\_info.rollover\_period} + \mathrm{TDC\_DATA_{hit}}) \\
                &\times \texttt{timetagger4\_param\_info.binsize}
            \end{align*}

            \item \ttdef{HIT\tu FLAG\tu RISING}~\texttt{1}~$\leftrightarrow$ Bit\,4\\
            Bit 4: Set if this hit is a rising edge. Otherwise, this
            word belongs to a falling edge.
        
        \end{itemize}

        Bits 3 down to 0:
        The channel number is given in the lowest nibble of the data word. A
        value of {0} corresponds to channel A, a value of {3}
        to channel D.\\
    }{
        \begin{itemize}
            \item\ttdef{HIT\tu FLAG\tu FPGA\tu MISSING}~8~$\leftrightarrow$ Bit\,7\\
            \ttdef{HIT\tu FLAG\tu COARSE\tu TIMESTAMP}~4~$\leftrightarrow$ Bit\,6\\
            Bit 7, 6: Resolution of this measurement\ifxHPTDC{}{ (see
            Section~\ref{difficulthits})}.\par
            \begin{small}
            \begin{tabular}{|c|c||l|}
                \hline
                bit 7 & bit 6 & Measurement Type \\\hline\hline
                0 & 0 &  Normal full resolution measurement.\\\hline
                0 & 1 &  Measurement performed with carry chain TDC at about \SI{150}{\pico\second} resolution.\\\hline
                1 & 0 &  Full resolution measurement that might in the wrong place in the data stream.\\\hline
                1 & 1 &  Measurement with only $5/6$\,ns = $833.\overline{3}$\,ps resolution. \\\hline
            \end{tabular}
            \end{small}
            \item\ttdef{HIT\tu FLAG\tu TIME\tu OVERFLOW}~2~$\leftrightarrow$ Bit\,5\\
            Bit 5: Rollover. The time since start pulse exceeded the 24-bit range
            that can be encoded in a data word. This word does not encode a
            measurement.  Instead, the readout software should increment a rollover counter that can be used as the upper bits of consecutive time stamps.
            The counters should be reset for each packet.  The total offset of a
            hit in picoseconds can be computed by
            \begin{align*}
                \Delta T_{hit} = &\,(\text{\#rollovers} \times \texttt{xtdc4\_static\_info.rollover\tu period} + \mathrm{TDC\_DATA_{hit}}) \\
                &\times \texttt{xtdc4\_param\_info.binsize}
            \end{align*}
            \item \indent\ttdef{HIT\tu FLAG\tu RISING}~1~$\leftrightarrow$ Bit\,4\\
            Bit 4: Set if this hit is a rising edge. Otherwise, this word belongs
            to a falling edge.  The channel number is given in the lowest nibble
            of the data word. \\
            A value of 0 corresponds to channel A, a value of 3 to channel D.\par
        \end{itemize}
    }
\end{description}